### 2020-01-20 rescience/manuscript.Rmd
Add draft (in progress) of rescience manuscript :pen:
also adds simple infrastructure

---
title: 'Reproducing "Fluctuation Domains"'
author: "Carl Boettiger"
date: "1/14/2020"
output: pdf_document
---

Computational reproducibility is

```{r include=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning=FALSE, error=FALSE, message = FALSE)
```

## Historical context

## Retrieval of software

I have changed laptops and the organizational schemes I use for my documents several times since publishing the original paper. Though I still have my original copy of the code for the manuscript sitting around somewhere in a compressed, encrypted archive blob that now lives on Amazon Glacier, accessing it there would have been complex and demanding.  Fortunately, in 2011 I uploaded a copy of this code to a dedicated repository on GitHub at <https://github.com/cboettig/fluctuationDomains>. I rely on this copy for the remainder of this reproducibility effort.

The published paper itself states that the code is available at the personal website of one of my co-authors, with URL <http://ecotheory.biology.gatech.edu/downloads/>.  Fortunately, this URL still resolves (my colleague is still at the same institution), and does indeed contain a downloadable zip file with a copy of the code. In 2012, I had uploaded a copy of this code as a supplement to Dryad, but both on my CV a the time and on my colleague's website we had recorded only the Dryad handle URL, <http://datadryad.org/handle/10255/dryad.37625>, which no longer resolves.  That handle can be resolved by the WayBackMachine, which doesn't contain the code archive but does reveal the DOI, <http://dx.doi.org/10.5061/dryad.j8n0p7vc>, which successfully resolves to the Dryad copy.  The code can also be found by searching the Dryad web interface for my surname (though it is listed as "data" and not "software."  In 2017, I had also imported the GitHub copy into the Zenodo data repository where it was again assigned a DOI and is identified as software in the metadata.  I note that the package was never submitted to the Central R Archive Network, CRAN.

Notably, these versions are not entirely the same.  The GitHub/Zenodo/Dryad version has the addition of a `configure.ac` script for autoconf, intended to make the package more portable in assisting with the linkage to the GSL library, which is missing from the original deposit (on the GeorgiaTech website and Dryad).  The GitHub version also lacked a copy of the `inst/` subdirectory, which contained a copy of the manuscript `.tex` file, original manuscript `.pdf` figures, and the R scripts that were supposed to generate these figures. (Though both versions include a `demo` directory that included similar code required to generate the figures, as discussed in the next section.)

## Execution

I had taken what I thought at the time would be appropriate steps to facilitate reproducibility, stating at the end of the manuscript:

>  In the spirit of scientifically reproducible research(Gentleman and Lang, 2007; Schwabet al., 2000; Stodden, 2009), we freely provide all the source code required to replicate the simulations and figuress hown in the text. Though the numerical simulations are written in C for computational efficiency, we provide a user interface and documentation by releasing all the code, figures, text, and examples as a software package for the widely used and freely available R statistical computing language. This package can be downloaded from http://ecotheory.biology.gatech.edu/downloads/.

Unfortunately, in attempting execution I ran into two significant obstacles that would have likely stopped a typical researcher unfamiliar with the details of the project.

First, the formally archived copy (GitHub/Dryad/Zenodo version) could not be installed directly due in fact to the autoconf `configure` script, which incorrectly states that it cannot find a version of the GNU Scientific Library (GSL) `>=1.8` (the version against which the package was originally built -- the current stable version is 2.6, see <http://git.savannah.gnu.org/cgit/gsl.git/tree/NEWS> for the changelog).  Ironically, the original GeorgiaTech archive version installed directly for me on both Mac and Linux platforms without any additional work (the default library linking flags in the provided `Makevars` file of the original source were sufficient.)  For instance, on a standard Ubuntu 18.04 (bionic) instance with `r-base`, and `libgsl-dev` installed from the `apt` repos, it was sufficient for me to run:

```
wget http://ecotheory.biology.gatech.edu/sites/default/files/adpaper_0.2-8.tar.gz
R CMD INSTALL adpaper_0.2-8.tar.gz
```

The same stategy worked on MacOSX (Catalina) with `gsl` installed via Homebrew. I was able to update the original autoconf script by recalling that it had been adapted from another package, the `gsl` R package <https://cran.r-project.org/web/packages/gsl/>, which also binds against the GSL library. Working from the autoconf files provided there, I could successfully get the package to configure and compile.  This highlights a potential risk in changes that are intended to make the package more portable but also add complexity.  More generally, while the package has no dependency on external R packages (beyond those default packages provided as part of base R: `stats`, `utils`, `graphics`, and `grDevices`, this issue illustrates the familiar reproducibility challenge that is created by changing versions of dependencies and system libraries (GSL in this case).  System libraries against which a package is compiled are particularly pernicious, because versioning of these components is both platform dependent and separate from the R package manager process, and thus cannot be addressed merely with package version tracking in tools such as `packrat` [@packrat] or `renv`.  Today, containerized approaches such a Docker [see @Boettiger2015; @Boettiger2017] provide a solution to this system-dependency issue that was not available a decade ago.

The second challenge was in figuring out just what commands had to be run to duplicate the figures.  As mentioned above, the GitHub version of the source-code did not have the manuscript source, and even the version that did have the mansucript source did not write the manuscript itself as a dynamic document (e.g. in Sweave [@Sweave]).  In that version, files `fig1.R` and `fig2.R` are were included in the same subdirectory as the `pdf` figures referenced by the `tex` version of the manuscript, but `fig2.R`, but these files contained only the code required to actually generate the figures themselves once the result data had been pre-computed and saved as `.txt` files. That result data files had also not been archived seperately.  Fortunately, re-reading my own documentation, I was able to deduce that these text files were generated by running the function `logistic()` with the parameter settings given in the caption of Fig 2 in the manuscript.

### Reproducibility

Running the `logistic()` function provided in the code, I was able to replicate the key results of the paper.  A few qualifications here are necessary.  The paper consists of two core results -- a  theoretical (i.e. derived analytically without computational component) which predicts the existance of 'fluctuation enhancement regimes' which can create substantial deviations from the dynamics predicted by the accepted theory at the time (that is, from the so-called canonical equation of adaptive dynamics), and a second result which relies on a computationally intensive stochastic ensemble simulation to illustrate these deviations arising for dynamics that begin in the "fluctation enhancement" regime.  These results are summarized by figures 1 and 2 of the original paper, which I reproduce here.

Reproducing figure 1 worked directly from the provided code, which merely plots equations derived from a little stochastic calculus as presented in the paper and appendix:

```{r}
library(fluctuationDomains)
## Figure 1 function definitions:
logistic_curve = function(x){-x*exp(-x*x/2)}
chemostat_curve <- function(x, d = 0.1, q = 0.1){
  (q*x-d/(1-x*d))* (d/x-2*d**2)
}
branching_curve <- function(x, SIGMA2_K = 2, SIGMA2_C = 1){
  -exp( (x^2/2)*(4/SIGMA2_C -1/SIGMA2_K) ) *
    (SIGMA2_C+exp(2*x^2/SIGMA2_C)*SIGMA2_C-2*SIGMA2_K)*x /
    ( (1+exp(2*x^2/SIGMA2_C)^2)*SIGMA2_C*SIGMA2_K)
}

landscape(logistic_curve, -3, 3)
landscape(chemostat_curve, 1, 9)
landscape(branching_curve, -.8, .8)
```

Figure 2 has the core computational results demonstrating the consequences of these fluctuation regimes.  The code for this analysis was implemented as pure C code, which can be run in stand-alone mode and generates three output text files.  The R package uses the `.C` interface to pass parameters to the C function (`Rlogistic`) which runs the ensemble and writes its output as text. The C function does not expose a random seed, so re-running the analysis creates results which are not bitwise identical each time. Of course the scientific results are expected to be independent of the seed anyway, so it is perhaps reassuring that as long as the ensemble of replicates is large enough, the same pattern can be reproduced quite closely. The original manuscript uses ensembles of 100,000 replicates, which I have reproduced here.  A possible source of confusion is that the code defaults to only 100 replicates if the ensemble size is not explicitly verified -- which is an ensemble small enough to still see random deviations from the predicted results.   I probably set that lower default to facilitate faster testing.  Likewise, the MAXTIME parameter has to be extended from the default setting to allow the third initial condition set to run sufficiently long.

```{r}
out = logistic(Xo = 1,  ENSEMBLES = 10^5, MAX_TIME = 5000)
```

```{r}
out = logistic(Xo = 2,  ENSEMBLES = 10^5, MAX_TIME = 5000)
```

```{r}
out = logistic(Xo = 3,  ENSEMBLES = 10^5, MAX_TIME = 10000)
```

Note that in the modern standard for R packages with methods in implemented in C, several things would be different from my original implementation.  The C methods are expected to bind R's random number generator engines, and not use their own methods, which allows them to coordinate with standard R methods for setting seed and so forth.  Also, the data should be passed by reference back to R and not serialized to disk (though this can introduce memory constraints).  Third, it is now also standard practice to register the C routines explicitly.  The built-in CHECK methods of R will flag these issues.

While the package is organized as an R package, it is worth noting that it is also not written up to the standards required of modern R packages to pass the built-in `R CMD check` testing routines successfully.  Some of these are not particularly material

- C routines are not registered
- `SystemRequirements` field was not provided in the package `DESCRIPTION`.  By adding this to list `libgsl`, it is possible to have the package successfully install on the `rhub` [@rhub] testing platforms.
- The package does not use the R random number generator.  This was intentional, as the package was written as stand-alone C code that happened to have an R interface, though notably even the C implementation fails to expose a random number `seed`. 
- missmatch in documentation and function definition

```{r}
```

### 2020-02-07 rescience/article.Rmd
Rendered article using ReScience LaTeX templates & fonts :pen:

--- 2020-01-20 rescience/manuscript.Rmd
@@
 title: 'Reproducing "Fluctuation Domains"'
-author: "Carl Boettiger"
-date: "1/14/2020"
-output: pdf_document
+output: 
+  pdf_document:
+    latex_engine: xelatex
+    template: rescience.latex
+    includes:
+      before_body: header.tex
+      after_body: suffix.tex
+    keep_tex: true
+documentclass: rescience
+bibliography: "bibliography.bib"
+
 ---
-
-Computational reproducibility is
 
@@
 ## Historical context
+
+In this analyis I seek to reproduce the numerical results of [@Boettiger2010], which focuses on the evolutionary trajectory of species trait under selection, as predicted by the so-called "Canonical Equation" of adaptive dynamics [@Dieckmann1996].
+Theoretical work I present in the paper predicts the emergence of a 'flutation enhancement' regime far from an evolutionary stable point, and suggests that the evolution of traits which start in this distant region would deviate substantially from the expected evolutionary path predicted by the canonical equation.
+In particular, the distribution of such trajectories could be bimodal, making the "canonical" path far from the most likely path.
+The details of this distribution cannot be solved for analytically however, so in this paper I resorted to an replicate exact stochastic simulations of the evolutionary model using a Gillespie algorithm [@Gillespie].
+
+I implemented Gillespie algorithm for the evolutionary model in C code, and wrapped the C code in an R package structure to make it easier to run and easier to plot results.
+The C code depended on one standard C library, the GNU Scientific Library, which has evolved considerably (with one major version change) since that time.
+The original source code was 'published' (initially only on a colleague's website, as stated in the paper, though later copies were submitted to formal archives, as discussed below).
+That original copy was distributed under a GPL v3 licence, though I later replaced that with a CC0 license when submitting the version to a data archive (Dryad) which required public domain declarations.
 
@@
 More generally, while the package has no dependency on external R packages (beyond those default packages provided as part of base R: `stats`, `utils`, `graphics`, and `grDevices`, this issue illustrates the familiar reproducibility challenge that is created by changing versions of dependencies and system libraries (GSL in this case).
-System libraries against which a package is compiled are particularly pernicious, because versioning of these components is both platform dependent and separate from the R package manager process, and thus cannot be addressed merely with package version tracking in tools such as `packrat` [@packrat] or `renv`.
+System libraries against which a package is compiled are particularly pernicious, because versioning of these components is both platform dependent and separate from the R package manager process, and thus cannot be addressed merely with package version tracking in tools such as `packrat` [@packrat] or `renv` [@renv].
 Today, containerized approaches such a Docker [see @Boettiger2015; @Boettiger2017] provide a solution to this system-dependency issue that was not available a decade ago.
@@
 As mentioned above, the GitHub version of the source-code did not have the manuscript source, and even the version that did have the mansucript source did not write the manuscript itself as a dynamic document (e.g.
-in Sweave [@Sweave]).
+in Sweave [@knitr_book]).
 In that version, files `fig1.R` and `fig2.R` are were included in the same subdirectory as the `pdf` figures referenced by the `tex` version of the manuscript, but `fig2.R`, but these files contained only the code required to actually generate the figures themselves once the result data had been pre-computed and saved as `.txt` files.
@@
 
-```{r}
+```{r fig1, fig.cap="The three panels of figure 1, showing examples of evolutionary landscapes and the corresponding fluctation domains for three classic models (logistic, chemostat, branching model).
+This figure is largely theoretical, and so easily replicates Figure 1 of the original paper.
+The first panel showing the logistic model depicts the fluctation regimes for the model parameters used in the numerical analysis."}
 library(fluctuationDomains)
@@
 
-Figure 2 has the core computational results demonstrating the consequences of these fluctuation regimes.
+Figure 2 of the original paper has the core computational results demonstrating the consequences of these fluctuation regimes.
 The code for this analysis was implemented as pure C code, which can be run in stand-alone mode and generates three output text files.
@@
 
-```{r}
-out = logistic(Xo = 1,  ENSEMBLES = 10^5, MAX_TIME = 5000)
+The code was never parallelized, but runs with a small memory footprint by streaming simulation data out (e.g.
+to disk) over `fprint`.
+Replicating all results takes about an hour of computational time on a Intel-i7 processor.
+
+```{r fig.cap = "A starting condition of Xo = 1, at the edge of the fluctuation dissipation regime.
+The whole evolutionary trajectory thus occurs within the dissipation regime, and mean dynamics closely match that of the canonical equation, and show a tight normal distribution around the expected path.
+This matches the trajectories seen figure 2 of the original manuscript."}
+out = logistic(Xo = 1,  ENSEMBLES = 10^5, MAX_TIME = 3000)
 ```
 
-```{r}
+```{r fig.cap="A starting condition of Xo = 2, matching the trajectories seen figure 2 of the original manuscript.
+Deviations from the canonical path are visible, but the distribution is not yet bimodal."}
 out = logistic(Xo = 2,  ENSEMBLES = 10^5, MAX_TIME = 5000)
@@
 
-```{r}
+```{r fig.cap="Starting deep in the predicted fluctuation enhancement regime, Xo = 3, the resulting distribution of trajectories is bimodal, just as shown in the original figure 2 of the original manuscript."}
 out = logistic(Xo = 3,  ENSEMBLES = 10^5, MAX_TIME = 10000)
@@
 
-Note that in the modern standard for R packages with methods in implemented in C, several things would be different from my original implementation.
-The C methods are expected to bind R's random number generator engines, and not use their own methods, which allows them to coordinate with standard R methods for setting seed and so forth.
-Also, the data should be passed by reference back to R and not serialized to disk (though this can introduce memory constraints).
-Third, it is now also standard practice to register the C routines explicitly.
-The built-in CHECK methods of R will flag these issues.
+### On the R package compendium
 
-While the package is organized as an R package, it is worth noting that it is also not written up to the standards required of modern R packages to pass the built-in `R CMD check` testing routines successfully.
-Some of these are not particularly material
+My original paper acknowledges the use of the R package compendium approach [@TempleLang2007] for reproducible research, and idea later developed in @Marwick.
+While a decade ago the package as created would pass R's built-in `R CMD check` routine, standards have since evolved and the current implementation would not do so:
 
-- C routines are not registered
+- The C methods are expected to bind R's random number generator engines, and not use their own methods, which allows them to coordinate with standard R methods for setting seed and so forth.   
+- Data should be passed by reference back to R and not serialized to disk (though this can introduce memory constraints).  
+- It is now also standard practice to register the C routines explicitly.  
 - `SystemRequirements` field was not provided in the package `DESCRIPTION`.
 By adding this to list `libgsl`, it is possible to have the package successfully install on the `rhub` [@rhub] testing platforms.
-- The package does not use the R random number generator.
-This was intentional, as the package was written as stand-alone C code that happened to have an R interface, though notably even the C implementation fails to expose a random number `seed`.
-- missmatch in documentation and function definition
 
-```{r}
-```
+Note that these tighter integrations would also prevent the C libraries from running as purely stand-alone implementation.
+In any event, meeting all the automated checks of a formal package is not an expectation of the compendium approach, which merely borrows some of the package tooling.
+
+A dynamic document using RMarkdown [@rmarkdown] for reproducing the present mansucript can be found in the `rescience` sub-directory which I have now added to the GitHub repository housing the original R package, <https://github.com/cboettig/fluctuationDomains>, git tag `rescience-submission`, now archived with DOI <https://doi.org/xxxx>.
+
+# Conclusions
+
+In conclusion, I have been able to successfully replicate the original results.
+As the original results were not performed with a fixed random seed, replicated results are statistically comparable but not bitwise identical.
+In a scientific sense this is perhaps more useful than replication with a fixed seed.
+My compendium approach did not install entirely out of the box, as an autoconf configure script first required updating.
+Ironically, the original version of the code published on a co-author's personal website and linked from the manuscript both still existed and did install out-of-the-box.
+Reproducing the results of the paper required some careful reading of parameters listed in the paper and manually knowing what functions to call, as this paper did not include a complete "dynamic document" [@knitr; @knitr_book; @rmarkdown] approach discussed in @Marwick and also used in this replication paper.
+I think this experience underscored the critical role dependency management has in frustrating reproducibility: this replication was relatively simple in part due to the low number of dependencies and the technical simplicity of the code.
+The other take-away for me is how easy it is to leave out small but important steps needed to reproduce a figure when not using the dynamic document approach.
+Despite having R scripts called "figure1.R" and "figure2.R", these scripts could not simply be run by themselves to create the figures.
+
+# References

### 2020-02-07 rescience/manuscript.tex
Rendered article using ReScience LaTeX templates & fonts :pen:

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{rescience}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Reproducing ``Fluctuation Domains''},
%  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Reproducing ``Fluctuation Domains''}
%\author{}
%\date{}

\begin{document}
\maketitle

%% ----------------------------------------------------------------------------
%% ReScience article template
%% Copyright (c) 2018 N.P. Rougier,
%% Released under a Creative Commons Attribution 4.0 International license.
%% ----------------------------------------------------------------------------

%% --- Top left header --------------------------------------------------------
\begin{tikzpicture}[remember picture, overlay]
  \node [shape=rectangle, draw=darkred, fill=darkred, yshift=-34mm,
        anchor=north west, minimum width=3.75cm, minimum height=10mm]
        at (current page.north west) {};
  \node [text=white, anchor=center, yshift=-39mm, xshift=1.875cm]
         at (current page.north west) {\small \SpaceRoboto RESCIENCE C};
\end{tikzpicture}

%% --- Title -------------------------------------------------------------------
{\let\newpage\relax\maketitle} \maketitle

%% --- Margin information -----------------------------------------------------
\marginnote{
  \footnotesize \sffamily
  \textbf{Edited by}\\
  \ifdefempty{\editorNAME}{\textcolor{darkgray}{(Editor)}}
             {\editorNAME\ifdefempty{\editorORCID}{}{$^{\orcid{\editorORCID}}$}}\\
  ~\\
  %%
  \ifdefempty{\reviewerINAME}{}
  {
  \textbf{Reviewed by}\\
  \ifdefempty{\reviewerINAME}{\textcolor{darkgray}{}}
             {\reviewerINAME\ifdefempty{\reviewerIORCID}{}{$^{\orcid{\reviewerIORCID}}$}\\}
  \ifdefempty{\reviewerIINAME}{\textcolor{darkgray}{}}
             {\reviewerIINAME\ifdefempty{\reviewerIIORCID}{}{$^{\orcid{\reviewerIIORCID}}$}\\}
  ~\\
  }
  %%
  \textbf{Received}\\
  \ifdefempty{\dateRECEIVED}{---}{\dateRECEIVED}\\
  ~\\
  %%
  \textbf{Published}\\
  \ifdefempty{\datePUBLISHED}{---}{\datePUBLISHED}\\
  ~\\
  %%
  \textbf{DOI}\\
  \ifdefempty{\articleDOI}{---}{\articleDOI}
}

%% --- Bottom statement -------------------------------------------------------
\newcommand{\container}[1]{\def\@container{#1}}
\begin{container}
  \afterpage {
    \begin{statement}
      \scriptsize \sffamily
      \hrule \vskip .5em
      Copyright © \articleYEAR~\authorsABBRV,
      released under a Creative Commons Attribution 4.0 International license.

      Correspondence should be addressed to
      \contactNAME~(\href{mailto:\contactEMAIL}{\contactEMAIL})

      The authors have declared that no competing interests exists.

      \ifdefempty{\codeURL}{}
      {Code is available at
      \href{\codeURL}{\detokenize\expandafter{\codeURL}}\ifdefempty{\codeDOI}{.}{ -- DOI \doi{\codeDOI}.}\ifdefempty{\codeSWH}{.}{ -- SWH  \href{https://archive.softwareheritage.org/\codeSWH/}{\detokenize\expandafter{\codeSWH}}.}}

      \ifdefempty{\dataURL}{}
      {Data is available at
      \href{\dataURL}{\detokenize\expandafter{\dataURL}}\ifdefempty{\dataDOI}{.}{ -- DOI \doi{\dataDOI}.}}

      \ifdefempty{\reviewURL}{}
     {Open peer review is available at \href{\reviewURL}{\detokenize\expandafter{\reviewURL}}.}
    \end{statement}
  }
\end{container}

%% --- Abstract ---------------------------------------------------------------
 \ifdefempty{\articleABSTRACT}{}{
   {\small \sffamily \textbf{Abstract} \articleABSTRACT \par}
 }

%% --- Replication ------------------------------------------------------------
 \ifdefempty{\replicationBIB}{}{
   {\small \sffamily \bfseries A replication of}
   \ifdefempty{\replicationURL}
        {\href{http://doi.org/\replicationDOI}{\small \sffamily \replicationBIB}}
        {\href{\replicationURL}{\small \sffamily \replicationBIB}}.
 \par }

\hypertarget{historical-context}{%
\subsection{Historical context}\label{historical-context}}

In this analyis I seek to reproduce the numerical results of (Boettiger,
Dushoff, and Weitz 2010), which focuses on the evolutionary trajectory
of species trait under selection, as predicted by the so-called
``Canonical Equation'' of adaptive dynamics (Dieckmann and Law 1996).
Theoretical work I present in the paper predicts the emergence of a
`flutation enhancement' regime far from an evolutionary stable point,
and suggests that the evolution of traits which start in this distant
region would deviate substantially from the expected evolutionary path
predicted by the canonical equation. In particular, the distribution of
such trajectories could be bimodal, making the ``canonical'' path far
from the most likely path. The details of this distribution cannot be
solved for analytically however, so in this paper I resorted to an
replicate exact stochastic simulations of the evolutionary model using a
Gillespie algorithm (Gillespie 1977).

I implemented Gillespie algorithm for the evolutionary model in C code,
and wrapped the C code in an R package structure to make it easier to
run and easier to plot results. The C code depended on one standard C
library, the GNU Scientific Library, which has evolved considerably
(with one major version change) since that time. The original source
code was `published' (initially only on a colleague's website, as stated
in the paper, though later copies were submitted to formal archives, as
discussed below). That original copy was distributed under a GPL v3
licence, though I later replaced that with a CC0 license when submitting
the version to a data archive (Dryad) which required public domain
declarations.

\hypertarget{retrieval-of-software}{%
\subsection{Retrieval of software}\label{retrieval-of-software}}

I have changed laptops and the organizational schemes I use for my
documents several times since publishing the original paper. Though I
still have my original copy of the code for the manuscript sitting
around somewhere in a compressed, encrypted archive blob that now lives
on Amazon Glacier, accessing it there would have been complex and
demanding. Fortunately, in 2011 I uploaded a copy of this code to a
dedicated repository on GitHub at
\url{https://github.com/cboettig/fluctuationDomains}. I rely on this
copy for the remainder of this reproducibility effort.

The published paper itself states that the code is available at the
personal website of one of my co-authors, with URL
\url{http://ecotheory.biology.gatech.edu/downloads/}. Fortunately, this
URL still resolves (my colleague is still at the same institution), and
does indeed contain a downloadable zip file with a copy of the code. In
2012, I had uploaded a copy of this code as a supplement to Dryad, but
both on my CV a the time and on my colleague's website we had recorded
only the Dryad handle URL,
\url{http://datadryad.org/handle/10255/dryad.37625}, which no longer
resolves. That handle can be resolved by the WayBackMachine, which
doesn't contain the code archive but does reveal the DOI,
\url{http://dx.doi.org/10.5061/dryad.j8n0p7vc}, which successfully
resolves to the Dryad copy. The code can also be found by searching the
Dryad web interface for my surname (though it is listed as ``data'' and
not ``software.'' In 2017, I had also imported the GitHub copy into the
Zenodo data repository where it was again assigned a DOI and is
identified as software in the metadata. I note that the package was
never submitted to the Central R Archive Network, CRAN.

Notably, these versions are not entirely the same. The
GitHub/Zenodo/Dryad version has the addition of a \texttt{configure.ac}
script for autoconf, intended to make the package more portable in
assisting with the linkage to the GSL library, which is missing from the
original deposit (on the GeorgiaTech website and Dryad). The GitHub
version also lacked a copy of the \texttt{inst/} subdirectory, which
contained a copy of the manuscript \texttt{.tex} file, original
manuscript \texttt{.pdf} figures, and the R scripts that were supposed
to generate these figures. (Though both versions include a \texttt{demo}
directory that included similar code required to generate the figures,
as discussed in the next section.)

\hypertarget{execution}{%
\subsection{Execution}\label{execution}}

I had taken what I thought at the time would be appropriate steps to
facilitate reproducibility, stating at the end of the manuscript:

\begin{quote}
In the spirit of scientifically reproducible research(Gentleman and
Lang, 2007; Schwabet al., 2000; Stodden, 2009), we freely provide all
the source code required to replicate the simulations and figuress hown
in the text. Though the numerical simulations are written in C for
computational efficiency, we provide a user interface and documentation
by releasing all the code, figures, text, and examples as a software
package for the widely used and freely available R statistical computing
language. This package can be downloaded from
\url{http://ecotheory.biology.gatech.edu/downloads/}.
\end{quote}

Unfortunately, in attempting execution I ran into two significant
obstacles that would have likely stopped a typical researcher unfamiliar
with the details of the project.

First, the formally archived copy (GitHub/Dryad/Zenodo version) could
not be installed directly due in fact to the autoconf \texttt{configure}
script, which incorrectly states that it cannot find a version of the
GNU Scientific Library (GSL) \texttt{\textgreater{}=1.8} (the version
against which the package was originally built -- the current stable
version is 2.6, see
\url{http://git.savannah.gnu.org/cgit/gsl.git/tree/NEWS} for the
changelog). Ironically, the original GeorgiaTech archive version
installed directly for me on both Mac and Linux platforms without any
additional work (the default library linking flags in the provided
\texttt{Makevars} file of the original source were sufficient.) For
instance, on a standard Ubuntu 18.04 (bionic) instance with
\texttt{r-base}, and \texttt{libgsl-dev} installed from the \texttt{apt}
repos, it was sufficient for me to run:

\begin{verbatim}
wget http://ecotheory.biology.gatech.edu/sites/default/files/adpaper_0.2-8.tar.gz
R CMD INSTALL adpaper_0.2-8.tar.gz
\end{verbatim}

The same stategy worked on MacOSX (Catalina) with \texttt{gsl} installed
via Homebrew. I was able to update the original autoconf script by
recalling that it had been adapted from another package, the
\texttt{gsl} R package
\url{https://cran.r-project.org/web/packages/gsl/}, which also binds
against the GSL library. Working from the autoconf files provided there,
I could successfully get the package to configure and compile. This
highlights a potential risk in changes that are intended to make the
package more portable but also add complexity. More generally, while the
package has no dependency on external R packages (beyond those default
packages provided as part of base R: \texttt{stats}, \texttt{utils},
\texttt{graphics}, and \texttt{grDevices}, this issue illustrates the
familiar reproducibility challenge that is created by changing versions
of dependencies and system libraries (GSL in this case). System
libraries against which a package is compiled are particularly
pernicious, because versioning of these components is both platform
dependent and separate from the R package manager process, and thus
cannot be addressed merely with package version tracking in tools such
as \texttt{packrat} (Ushey et al. 2018) or \texttt{renv} (Ushey 2019).
Today, containerized approaches such a Docker (see Boettiger 2015;
Boettiger and Eddelbuettel 2017) provide a solution to this
system-dependency issue that was not available a decade ago.

The second challenge was in figuring out just what commands had to be
run to duplicate the figures. As mentioned above, the GitHub version of
the source-code did not have the manuscript source, and even the version
that did have the mansucript source did not write the manuscript itself
as a dynamic document (e.g.~in Sweave (Xie 2015)). In that version,
files \texttt{fig1.R} and \texttt{fig2.R} are were included in the same
subdirectory as the \texttt{pdf} figures referenced by the \texttt{tex}
version of the manuscript, but \texttt{fig2.R}, but these files
contained only the code required to actually generate the figures
themselves once the result data had been pre-computed and saved as
\texttt{.txt} files. That result data files had also not been archived
seperately. Fortunately, re-reading my own documentation, I was able to
deduce that these text files were generated by running the function
\texttt{logistic()} with the parameter settings given in the caption of
Fig 2 in the manuscript.

\hypertarget{reproducibility}{%
\subsubsection{Reproducibility}\label{reproducibility}}

Running the \texttt{logistic()} function provided in the code, I was
able to replicate the key results of the paper. A few qualifications
here are necessary. The paper consists of two core results -- a
theoretical (i.e.~derived analytically without computational component)
which predicts the existance of `fluctuation enhancement regimes' which
can create substantial deviations from the dynamics predicted by the
accepted theory at the time (that is, from the so-called canonical
equation of adaptive dynamics), and a second result which relies on a
computationally intensive stochastic ensemble simulation to illustrate
these deviations arising for dynamics that begin in the ``fluctation
enhancement'' regime. These results are summarized by figures 1 and 2 of
the original paper, which I reproduce here.

Reproducing figure 1 worked directly from the provided code, which
merely plots equations derived from a little stochastic calculus as
presented in the paper and appendix:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(fluctuationDomains)}
\CommentTok{## Figure 1 function definitions:}
\NormalTok{logistic_curve =}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x)\{}\OperatorTok{-}\NormalTok{x}\OperatorTok{*}\KeywordTok{exp}\NormalTok{(}\OperatorTok{-}\NormalTok{x}\OperatorTok{*}\NormalTok{x}\OperatorTok{/}\DecValTok{2}\NormalTok{)\}}
\NormalTok{chemostat_curve <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x, }\DataTypeTok{d =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{q =} \FloatTok{0.1}\NormalTok{)\{}
\NormalTok{  (q}\OperatorTok{*}\NormalTok{x}\OperatorTok{-}\NormalTok{d}\OperatorTok{/}\NormalTok{(}\DecValTok{1}\OperatorTok{-}\NormalTok{x}\OperatorTok{*}\NormalTok{d))}\OperatorTok{*}\StringTok{ }\NormalTok{(d}\OperatorTok{/}\NormalTok{x}\DecValTok{-2}\OperatorTok{*}\NormalTok{d}\OperatorTok{**}\DecValTok{2}\NormalTok{)}
\NormalTok{\}}
\NormalTok{branching_curve <-}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x, }\DataTypeTok{SIGMA2_K =} \DecValTok{2}\NormalTok{, }\DataTypeTok{SIGMA2_C =} \DecValTok{1}\NormalTok{)\{}
  \OperatorTok{-}\KeywordTok{exp}\NormalTok{( (x}\OperatorTok{^}\DecValTok{2}\OperatorTok{/}\DecValTok{2}\NormalTok{)}\OperatorTok{*}\NormalTok{(}\DecValTok{4}\OperatorTok{/}\NormalTok{SIGMA2_C }\DecValTok{-1}\OperatorTok{/}\NormalTok{SIGMA2_K) ) }\OperatorTok{*}
\StringTok{    }\NormalTok{(SIGMA2_C}\OperatorTok{+}\KeywordTok{exp}\NormalTok{(}\DecValTok{2}\OperatorTok{*}\NormalTok{x}\OperatorTok{^}\DecValTok{2}\OperatorTok{/}\NormalTok{SIGMA2_C)}\OperatorTok{*}\NormalTok{SIGMA2_C}\DecValTok{-2}\OperatorTok{*}\NormalTok{SIGMA2_K)}\OperatorTok{*}\NormalTok{x }\OperatorTok{/}
\StringTok{    }\NormalTok{( (}\DecValTok{1}\OperatorTok{+}\KeywordTok{exp}\NormalTok{(}\DecValTok{2}\OperatorTok{*}\NormalTok{x}\OperatorTok{^}\DecValTok{2}\OperatorTok{/}\NormalTok{SIGMA2_C)}\OperatorTok{^}\DecValTok{2}\NormalTok{)}\OperatorTok{*}\NormalTok{SIGMA2_C}\OperatorTok{*}\NormalTok{SIGMA2_K)}
\NormalTok{\}}

\KeywordTok{landscape}\NormalTok{(logistic_curve, }\DecValTok{-3}\NormalTok{, }\DecValTok{3}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig1-1.pdf}
\caption{The three panels of figure 1, showing examples of evolutionary
landscapes and the corresponding fluctation domains for three classic
models (logistic, chemostat, branching model). This figure is largely
theoretical, and so easily replicates Figure 1 of the original paper.
The first panel showing the logistic model depicts the fluctation
regimes for the model parameters used in the numerical analysis.}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{landscape}\NormalTok{(chemostat_curve, }\DecValTok{1}\NormalTok{, }\DecValTok{9}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig1-2.pdf}
\caption{The three panels of figure 1, showing examples of evolutionary
landscapes and the corresponding fluctation domains for three classic
models (logistic, chemostat, branching model). This figure is largely
theoretical, and so easily replicates Figure 1 of the original paper.
The first panel showing the logistic model depicts the fluctation
regimes for the model parameters used in the numerical analysis.}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{landscape}\NormalTok{(branching_curve, }\FloatTok{-.8}\NormalTok{, }\FloatTok{.8}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/fig1-3.pdf}
\caption{The three panels of figure 1, showing examples of evolutionary
landscapes and the corresponding fluctation domains for three classic
models (logistic, chemostat, branching model). This figure is largely
theoretical, and so easily replicates Figure 1 of the original paper.
The first panel showing the logistic model depicts the fluctation
regimes for the model parameters used in the numerical analysis.}
\end{figure}

Figure 2 of the original paper has the core computational results
demonstrating the consequences of these fluctuation regimes. The code
for this analysis was implemented as pure C code, which can be run in
stand-alone mode and generates three output text files. The R package
uses the \texttt{.C} interface to pass parameters to the C function
(\texttt{Rlogistic}) which runs the ensemble and writes its output as
text. The C function does not expose a random seed, so re-running the
analysis creates results which are not bitwise identical each time. Of
course the scientific results are expected to be independent of the seed
anyway, so it is perhaps reassuring that as long as the ensemble of
replicates is large enough, the same pattern can be reproduced quite
closely. The original manuscript uses ensembles of 100,000 replicates,
which I have reproduced here. A possible source of confusion is that the
code defaults to only 100 replicates if the ensemble size is not
explicitly verified -- which is an ensemble small enough to still see
random deviations from the predicted results. I probably set that lower
default to facilitate faster testing. Likewise, the MAXTIME parameter
has to be extended from the default setting to allow the third initial
condition set to run sufficiently long.

The code was never parallelized, but runs with a small memory footprint
by streaming simulation data out (e.g.~to disk) over \texttt{fprint}.
Replicating all results takes about an hour of computational time on a
Intel-i7 processor.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out =}\StringTok{ }\KeywordTok{logistic}\NormalTok{(}\DataTypeTok{Xo =} \DecValTok{1}\NormalTok{,  }\DataTypeTok{ENSEMBLES =} \DecValTok{10}\OperatorTok{^}\DecValTok{5}\NormalTok{, }\DataTypeTok{MAX_TIME =} \DecValTok{3000}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{A starting condition of Xo = 1, at the edge of the fluctuation
dissipation regime. The whole evolutionary trajectory thus occurs within
the dissipation regime, and mean dynamics closely match that of the
canonical equation, and show a tight normal distribution around the
expected path. This matches the trajectories seen figure 2 of the
original manuscript.}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out =}\StringTok{ }\KeywordTok{logistic}\NormalTok{(}\DataTypeTok{Xo =} \DecValTok{2}\NormalTok{,  }\DataTypeTok{ENSEMBLES =} \DecValTok{10}\OperatorTok{^}\DecValTok{5}\NormalTok{, }\DataTypeTok{MAX_TIME =} \DecValTok{5000}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{A starting condition of Xo = 2, matching the trajectories seen
figure 2 of the original manuscript. Deviations from the canonical path
are visible, but the distribution is not yet bimodal.}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{out =}\StringTok{ }\KeywordTok{logistic}\NormalTok{(}\DataTypeTok{Xo =} \DecValTok{3}\NormalTok{,  }\DataTypeTok{ENSEMBLES =} \DecValTok{10}\OperatorTok{^}\DecValTok{5}\NormalTok{, }\DataTypeTok{MAX_TIME =} \DecValTok{10000}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Starting deep in the predicted fluctuation enhancement regime,
Xo = 3, the resulting distribution of trajectories is bimodal, just as
shown in the original figure 2 of the original manuscript.}
\end{figure}

\hypertarget{on-the-r-package-compendium}{%
\subsubsection{On the R package
compendium}\label{on-the-r-package-compendium}}

My original paper acknowledges the use of the R package compendium
approach (Gentleman and Temple Lang 2007) for reproducible research, and
idea later developed in Marwick, Boettiger, and Mullen (2018). While a
decade ago the package as created would pass R's built-in
\texttt{R\ CMD\ check} routine, standards have since evolved and the
current implementation would not do so:

\begin{itemize}
\tightlist
\item
  The C methods are expected to bind R's random number generator
  engines, and not use their own methods, which allows them to
  coordinate with standard R methods for setting seed and so forth.\\
\item
  Data should be passed by reference back to R and not serialized to
  disk (though this can introduce memory constraints).\\
\item
  It is now also standard practice to register the C routines
  explicitly.\\
\item
  \texttt{SystemRequirements} field was not provided in the package
  \texttt{DESCRIPTION}. By adding this to list \texttt{libgsl}, it is
  possible to have the package successfully install on the \texttt{rhub}
  (Csárdi and Salmon 2019) testing platforms.
\end{itemize}

Note that these tighter integrations would also prevent the C libraries
from running as purely stand-alone implementation. In any event, meeting
all the automated checks of a formal package is not an expectation of
the compendium approach, which merely borrows some of the package
tooling.

A dynamic document using RMarkdown (Xie, Allaire, and Grolemund 2018)
for reproducing the present mansucript can be found in the
\texttt{rescience} sub-directory which I have now added to the GitHub
repository housing the original R package,
\url{https://github.com/cboettig/fluctuationDomains}, git tag
\texttt{rescience-submission}, now archived with DOI
\url{https://doi.org/xxxx}.

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

In conclusion, I have been able to successfully replicate the original
results. As the original results were not performed with a fixed random
seed, replicated results are statistically comparable but not bitwise
identical. In a scientific sense this is perhaps more useful than
replication with a fixed seed. My compendium approach did not install
entirely out of the box, as an autoconf configure script first required
updating. Ironically, the original version of the code published on a
co-author's personal website and linked from the manuscript both still
existed and did install out-of-the-box. Reproducing the results of the
paper required some careful reading of parameters listed in the paper
and manually knowing what functions to call, as this paper did not
include a complete ``dynamic document'' (Xie 2014, 2015; Xie, Allaire,
and Grolemund 2018) approach discussed in Marwick, Boettiger, and Mullen
(2018) and also used in this replication paper. I think this experience
underscored the critical role dependency management has in frustrating
reproducibility: this replication was relatively simple in part due to
the low number of dependencies and the technical simplicity of the code.
The other take-away for me is how easy it is to leave out small but
important steps needed to reproduce a figure when not using the dynamic
document approach. Despite having R scripts called ``figure1.R'' and
``figure2.R'', these scripts could not simply be run by themselves to
create the figures.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Boettiger2015}{}%
Boettiger, Carl. 2015. ``An Introduction to Docker for Reproducible
Research.'' \emph{ACM SIGOPS Operating Systems Review} 49 (1): 71--79.
\url{https://doi.org/10.1145/2723872.2723882}.

\leavevmode\hypertarget{ref-Boettiger2010}{}%
Boettiger, Carl, Jonathan Dushoff, and Joshua S. Weitz. 2010.
``Fluctuation Domains in Adaptive Evolution.'' \emph{Theoretical
Population Biology} 77 (1): 6--13.
\url{https://doi.org/10.1016/j.tpb.2009.10.003}.

\leavevmode\hypertarget{ref-Boettiger2017}{}%
Boettiger, Carl, and Dirk Eddelbuettel. 2017. ``An Introduction to
Rocker: Docker Containers for R.'' \emph{The R Journal} 9 (2): 527.
\url{https://doi.org/10.32614/RJ-2017-065}.

\leavevmode\hypertarget{ref-rhub}{}%
Csárdi, Gábor, and Maëlle Salmon. 2019. \emph{Rhub: Connect to 'R-Hub'}.
\url{https://CRAN.R-project.org/package=rhub}.

\leavevmode\hypertarget{ref-Dieckmann1996}{}%
Dieckmann, Ulf, and Richard Law. 1996. ``The Dynamical Theory of
Coevolution: A Derivation from Stochastic Ecological Processes.''
\emph{Journal of Mathematical Biology} 34 (5-6): 579--612.
\url{https://doi.org/10.1007/BF02409751}.

\leavevmode\hypertarget{ref-TempleLang2007}{}%
Gentleman, Robert, and Duncan Temple Lang. 2007. ``Statistical Analyses
and Reproducible Research.'' \emph{Journal of Computational and
Graphical Statistics} 16 (1): 1--23.
\url{https://doi.org/10.1198/106186007X178663}.

\leavevmode\hypertarget{ref-Gillespie}{}%
Gillespie, Daniel. 1977. ``Exact Stochastic Simulation of Coupled
Chemical Reactions.'' \emph{Journal of Physical Chemistry} 81.25:
2340--61.

\leavevmode\hypertarget{ref-Marwick}{}%
Marwick, Ben, Carl Boettiger, and Lincoln Mullen. 2018. ``Packaging Data
Analytical Work Reproducibly Using R (and Friends).'' \emph{The American
Statistician} 72 (1): 80--88.
\url{https://doi.org/10.1080/00031305.2017.1375986}.

\leavevmode\hypertarget{ref-renv}{}%
Ushey, Kevin. 2019. \emph{Renv: Project Environments}.
\url{https://CRAN.R-project.org/package=renv}.

\leavevmode\hypertarget{ref-packrat}{}%
Ushey, Kevin, Jonathan McPherson, Joe Cheng, Aron Atkins, and JJ
Allaire. 2018. \emph{Packrat: A Dependency Management System for
Projects and Their R Package Dependencies}.
\url{https://CRAN.R-project.org/package=packrat}.

\leavevmode\hypertarget{ref-knitr}{}%
Xie, Yihui. 2014. ``Knitr: A Comprehensive Tool for Reproducible
Research in R.'' In \emph{Implementing Reproducible Computational
Research}, edited by Victoria Stodden, Friedrich Leisch, and Roger D.
Peng. Chapman; Hall/CRC.
\url{http://www.crcpress.com/product/isbn/9781466561595}.

\leavevmode\hypertarget{ref-knitr_book}{}%
---------. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca
Raton, Florida: Chapman; Hall/CRC. \url{https://yihui.org/knitr/}.

\leavevmode\hypertarget{ref-rmarkdown}{}%
Xie, Yihui, J.J. Allaire, and Garrett Grolemund. 2018. \emph{R Markdown:
The Definitive Guide}. Boca Raton, Florida: Chapman; Hall/CRC.
\url{https://bookdown.org/yihui/rmarkdown}.

\hypersetup{linkcolor=black,urlcolor=darkgray}
\renewcommand\emph[1]{{\bfseries #1}}
\setlength\bibitemsep{0pt}
\printbibliography

\end{document}

### 2020-02-18 rescience/manuscript.tex
Fix some typos

@@
 
-In this analyis I seek to reproduce the numerical results of (Boettiger,
+In this analysis I seek to reproduce the numerical results of (Boettiger,
 Dushoff, and Weitz 2010), which focuses on the evolutionary trajectory
@@
 2012, I had uploaded a copy of this code as a supplement to Dryad, but
-both on my CV a the time and on my colleague's website we had recorded
+both on my CV at the time and on my colleague's website we had recorded
 only the Dryad handle URL,
@@
 Lang, 2007; Schwabet al., 2000; Stodden, 2009), we freely provide all
-the source code required to replicate the simulations and figuress hown
+the source code required to replicate the simulations and figures shown
 in the text. Though the numerical simulations are written in C for
@@
 
-The same stategy worked on MacOSX (Catalina) with \texttt{gsl} installed
+The same strategy worked on MacOSX (Catalina) with \texttt{gsl} installed
 via Homebrew. I was able to update the original autoconf script by
@@
 as \texttt{packrat} (Ushey et al. 2018) or \texttt{renv} (Ushey 2019).
-Today, containerized approaches such a Docker (see Boettiger 2015;
+Today, containerized approaches such as Docker (see Boettiger 2015;
 Boettiger and Eddelbuettel 2017) provide a solution to this
@@
 the source-code did not have the manuscript source, and even the version
-that did have the mansucript source did not write the manuscript itself
+that did have the manuscript source did not write the manuscript itself
 as a dynamic document (e.g.~in Sweave (Xie 2015)). In that version,
@@
 subdirectory as the \texttt{pdf} figures referenced by the \texttt{tex}
-version of the manuscript, but \texttt{fig2.R}, but these files
+version of the manuscript, but these files
 contained only the code required to actually generate the figures
 themselves once the result data had been pre-computed and saved as
-\texttt{.txt} files. That result data files had also not been archived
-seperately. Fortunately, re-reading my own documentation, I was able to
+\texttt{.txt} files. The result data files had also not been archived
+separately. Fortunately, re-reading my own documentation, I was able to
 deduce that these text files were generated by running the function
@@
 theoretical (i.e.~derived analytically without computational component)
-which predicts the existance of `fluctuation enhancement regimes' which
+which predicts the existence of `fluctuation enhancement regimes' which
 can create substantial deviations from the dynamics predicted by the
@@
 computationally intensive stochastic ensemble simulation to illustrate
-these deviations arising for dynamics that begin in the ``fluctation
+these deviations arising for dynamics that begin in the ``fluctuation
 enhancement'' regime. These results are summarized by figures 1 and 2 of
@@
 \caption{The three panels of figure 1, showing examples of evolutionary
-landscapes and the corresponding fluctation domains for three classic
+landscapes and the corresponding fluctuation domains for three classic
 models (logistic, chemostat, branching model). This figure is largely
 theoretical, and so easily replicates Figure 1 of the original paper.
-The first panel showing the logistic model depicts the fluctation
+The first panel showing the logistic model depicts the fluctuation
 regimes for the model parameters used in the numerical analysis.}
@@
 A dynamic document using RMarkdown (Xie, Allaire, and Grolemund 2018)
-for reproducing the present mansucript can be found in the
+for reproducing the present manuscript can be found in the
 \texttt{rescience} sub-directory which I have now added to the GitHub

### 2020-02-18 rescience/article.Rmd

@@
 
-In this analyis I seek to reproduce the numerical results of [@Boettiger2010], which focuses on the evolutionary trajectory of species trait under selection, as predicted by the so-called "Canonical Equation" of adaptive dynamics [@Dieckmann1996].
+In this analsyis I seek to reproduce the numerical results of [@Boettiger2010], which focuses on the evolutionary trajectory of species trait under selection, as predicted by the so-called "Canonical Equation" of adaptive dynamics [@Dieckmann1996].
 Theoretical work I present in the paper predicts the emergence of a 'flutation enhancement' regime far from an evolutionary stable point, and suggests that the evolution of traits which start in this distant region would deviate substantially from the expected evolutionary path predicted by the canonical equation.
@@
 Fortunately, this URL still resolves (my colleague is still at the same institution), and does indeed contain a downloadable zip file with a copy of the code.
-In 2012, I had uploaded a copy of this code as a supplement to Dryad, but both on my CV a the time and on my colleague's website we had recorded only the Dryad handle URL, <http://datadryad.org/handle/10255/dryad.37625>, which no longer resolves.
+In 2012, I had uploaded a copy of this code as a supplement to Dryad, but both on my CV at the time and on my colleague's website we had recorded only the Dryad handle URL, <http://datadryad.org/handle/10255/dryad.37625>, which no longer resolves.
 That handle can be resolved by the WayBackMachine, which doesn't contain the code archive but does reveal the DOI, <http://dx.doi.org/10.5061/dryad.j8n0p7vc>, which successfully resolves to the Dryad copy.
@@
 
->  In the spirit of scientifically reproducible research(Gentleman and Lang, 2007; Schwabet al., 2000; Stodden, 2009), we freely provide all the source code required to replicate the simulations and figuress hown in the text.
+>  In the spirit of scientifically reproducible research(Gentleman and Lang, 2007; Schwabet al., 2000; Stodden, 2009), we freely provide all the source code required to replicate the simulations and figures shown in the text.
 Though the numerical simulations are written in C for computational efficiency, we provide a user interface and documentation by releasing all the code, figures, text, and examples as a software package for the widely used and freely available R statistical computing language.
@@
 
-The same stategy worked on MacOSX (Catalina) with `gsl` installed via Homebrew.
+The same strategy worked on MacOSX (Catalina) with `gsl` installed via Homebrew.
 I was able to update the original autoconf script by recalling that it had been adapted from another package, the `gsl` R package <https://cran.r-project.org/web/packages/gsl/>, which also binds against the GSL library.
@@
 System libraries against which a package is compiled are particularly pernicious, because versioning of these components is both platform dependent and separate from the R package manager process, and thus cannot be addressed merely with package version tracking in tools such as `packrat` [@packrat] or `renv` [@renv].
-Today, containerized approaches such a Docker [see @Boettiger2015; @Boettiger2017] provide a solution to this system-dependency issue that was not available a decade ago.
+Today, containerized approaches such as Docker [see @Boettiger2015; @Boettiger2017] provide a solution to this system-dependency issue that was not available a decade ago.
 
 The second challenge was in figuring out just what commands had to be run to duplicate the figures.
-As mentioned above, the GitHub version of the source-code did not have the manuscript source, and even the version that did have the mansucript source did not write the manuscript itself as a dynamic document (e.g.
+As mentioned above, the GitHub version of the source-code did not have the manuscript source, and even the version that did have the manuscript source did not write the manuscript itself as a dynamic document (e.g.
 in Sweave [@knitr_book]).
-In that version, files `fig1.R` and `fig2.R` are were included in the same subdirectory as the `pdf` figures referenced by the `tex` version of the manuscript, but `fig2.R`, but these files contained only the code required to actually generate the figures themselves once the result data had been pre-computed and saved as `.txt` files.
-That result data files had also not been archived seperately.
+In that version, files `fig1.R` and `fig2.R` are were included in the same subdirectory as the `pdf` figures referenced by the `tex` version of the manuscript, but these files contained only the code required to actually generate the figures themselves once the result data had been pre-computed and saved as `.txt` files.
+The result data files had also not been archived separately.
 Fortunately, re-reading my own documentation, I was able to deduce that these text files were generated by running the function `logistic()` with the parameter settings given in the caption of Fig 2 in the manuscript.
@@
 The paper consists of two core results -- a  theoretical (i.e.
-derived analytically without computational component) which predicts the existance of 'fluctuation enhancement regimes' which can create substantial deviations from the dynamics predicted by the accepted theory at the time (that is, from the so-called canonical equation of adaptive dynamics), and a second result which relies on a computationally intensive stochastic ensemble simulation to illustrate these deviations arising for dynamics that begin in the "fluctation enhancement" regime.
+derived analytically without computational component) which predicts the existence of 'fluctuation enhancement regimes' which can create substantial deviations from the dynamics predicted by the accepted theory at the time (that is, from the so-called canonical equation of adaptive dynamics), and a second result which relies on a computationally intensive stochastic ensemble simulation to illustrate these deviations arising for dynamics that begin in the "fluctuation enhancement" regime.
 These results are summarized by figures 1 and 2 of the original paper, which I reproduce here.
@@
 
-```{r fig1, fig.cap="The three panels of figure 1, showing examples of evolutionary landscapes and the corresponding fluctation domains for three classic models (logistic, chemostat, branching model).
+```{r fig1, fig.cap="The three panels of figure 1, showing examples of evolutionary landscapes and the corresponding fluctuation domains for three classic models (logistic, chemostat, branching model).
 This figure is largely theoretical, and so easily replicates Figure 1 of the original paper.
-The first panel showing the logistic model depicts the fluctation regimes for the model parameters used in the numerical analysis."}
+The first panel showing the logistic model depicts the fluctuation regimes for the model parameters used in the numerical analysis."}
 library(fluctuationDomains)
@@
 
-A dynamic document using RMarkdown [@rmarkdown] for reproducing the present mansucript can be found in the `rescience` sub-directory which I have now added to the GitHub repository housing the original R package, <https://github.com/cboettig/fluctuationDomains>, git tag `rescience-submission`, now archived with DOI <https://doi.org/xxxx>.
+A dynamic document using RMarkdown [@rmarkdown] for reproducing the present manuscript can be found in the `rescience` sub-directory which I have now added to the GitHub repository housing the original R package, <https://github.com/cboettig/fluctuationDomains>, git tag `rescience-submission`, now archived with DOI <https://doi.org/xxxx>.
 

### 2020-02-19 rescience/article.Rmd
rebuild with spellcheck :abc:

@@
       after_body: suffix.tex
-    keep_tex: true
 documentclass: rescience
@@
 
-In this analsyis I seek to reproduce the numerical results of [@Boettiger2010], which focuses on the evolutionary trajectory of species trait under selection, as predicted by the so-called "Canonical Equation" of adaptive dynamics [@Dieckmann1996].
-Theoretical work I present in the paper predicts the emergence of a 'flutation enhancement' regime far from an evolutionary stable point, and suggests that the evolution of traits which start in this distant region would deviate substantially from the expected evolutionary path predicted by the canonical equation.
+In this analysis I seek to reproduce the numerical results of [@Boettiger2010], which focuses on the evolutionary trajectory of species trait under selection, as predicted by the so-called "Canonical Equation" of adaptive dynamics [@Dieckmann1996].
+Theoretical work I present in the paper predicts the emergence of a 'fluctuation enhancement' regime far from an evolutionary stable point, and suggests that the evolution of traits which start in this distant region would deviate substantially from the expected evolutionary path predicted by the canonical equation.
 In particular, the distribution of such trajectories could be bimodal, making the "canonical" path far from the most likely path.
@@
 The GitHub/Zenodo/Dryad version has the addition of a `configure.ac` script for autoconf, intended to make the package more portable in assisting with the linkage to the GSL library, which is missing from the original deposit (on the GeorgiaTech website and Dryad).
-The GitHub version also lacked a copy of the `inst/` subdirectory, which contained a copy of the manuscript `.tex` file, original manuscript `.pdf` figures, and the R scripts that were supposed to generate these figures.
+The GitHub version also lacked a copy of the `inst/` sub-directory, which contained a copy of the manuscript `.tex` file, original manuscript `.pdf` figures, and the R scripts that were supposed to generate these figures.
 (Though both versions include a `demo` directory that included similar code required to generate the figures, as discussed in the next section.)
@@
 in Sweave [@knitr_book]).
-In that version, files `fig1.R` and `fig2.R` are were included in the same subdirectory as the `pdf` figures referenced by the `tex` version of the manuscript, but these files contained only the code required to actually generate the figures themselves once the result data had been pre-computed and saved as `.txt` files.
+In that version, files `fig1.R` and `fig2.R` are were included in the same sub-directory as the `pdf` figures referenced by the `tex` version of the manuscript, but these files contained only the code required to actually generate the figures themselves once the result data had been pre-computed and saved as `.txt` files.
 The result data files had also not been archived separately.
@@
 The R package uses the `.C` interface to pass parameters to the C function (`Rlogistic`) which runs the ensemble and writes its output as text.
-The C function does not expose a random seed, so re-running the analysis creates results which are not bitwise identical each time.
+The C function does not expose a random seed, so re-running the analysis creates results which are not bit-wise identical each time.
 Of course the scientific results are expected to be independent of the seed anyway, so it is perhaps reassuring that as long as the ensemble of replicates is large enough, the same pattern can be reproduced quite closely.
@@
 
-Note that these tighter integrations would also prevent the C libraries from running as purely stand-alone implementation.
+Note that these tighter integration would also prevent the C libraries from running as purely stand-alone implementation.
 In any event, meeting all the automated checks of a formal package is not an expectation of the compendium approach, which merely borrows some of the package tooling.
@@
 In conclusion, I have been able to successfully replicate the original results.
-As the original results were not performed with a fixed random seed, replicated results are statistically comparable but not bitwise identical.
+As the original results were not performed with a fixed random seed, replicated results are statistically comparable but not bit-wise identical.
 In a scientific sense this is perhaps more useful than replication with a fixed seed.

### 2020-09-11 rescience/article.Rmd

@@
 
-```{r fig1, fig.cap="The three panels of figure 1, showing examples of evolutionary landscapes and the corresponding fluctuation domains for three classic models (logistic, chemostat, branching model).
+```{r fig1, fig.width = 5, fig.height = 3, fig.show = "hold", out.extra="", fig.cap="The three panels of figure 1, showing examples of evolutionary landscapes and the corresponding fluctuation domains for three classic models (logistic, chemostat, branching model).
 This figure is largely theoretical, and so easily replicates Figure 1 of the original paper.

### 2020-09-11 rescience/metadata.tex

% DO NOT EDIT - automatically generated from metadata.yaml

\def \codeURL{https://github.com/cboettig/fluctationDomains}
\def \codeDOI{}
\def \codeSWH{}
\def \dataURL{}
\def \dataDOI{}
\def \editorNAME{}
\def \editorORCID{}
\def \reviewerINAME{}
\def \reviewerIORCID{}
\def \reviewerIINAME{}
\def \reviewerIIORCID{}
\def \dateRECEIVED{}
\def \dateACCEPTED{}
\def \datePUBLISHED{}
\def \articleTITLE{[Re] Fluctation Domains}
\def \articleTYPE{Reproduction}
\def \articleDOMAIN{Ten Years Reproducibility Challenge}
\def \articleBIBLIOGRAPHY{bibliography.bib}
\def \articleYEAR{2020}
\def \reviewURL{}
\def \articleABSTRACT{A stochastic ensemble simulation of evolutionary dynamics has been successfully reproduced. Simulation code was in C and could be called from wrappers implemented as an R package.  Reproduction required minor modification to the configuration files for compatibility with newer versions of the GNU Scientific Library.}
\def \replicationCITE{Carl Boettiger, Jonathan Dushoff, Joshua S Weitz (2010). Fluctuation domains in adaptive evolution, Theoretical Population Biology 77 (1) 6-13. doi:10.1016/j.tpb.2009.10.003.}
\def \replicationBIB{Boettiger2010}
\def \replicationURL{https://arxiv.org/abs/1004.4233}
\def \replicationDOI{https://doi.org/10.1016/j.tpb.2009.10.003}
\def \contactNAME{Carl Boettiger}
\def \contactEMAIL{cboettig@berkeley.edu}
\def \articleKEYWORDS{ten years reproducibility challenge, R, C}
\def \journalNAME{ReScience C}
\def \journalVOLUME{5}
\def \journalISSUE{2}
\def \articleNUMBER{}
\def \articleDOI{}
\def \authorsFULL{Carl Boettiger}
\def \authorsABBRV{C. Boettiger}
\def \authorsSHORT{Boettiger}
\title{\articleTITLE}
\date{}
\author[1,\orcid{https://orcid.org/0000-0002-1642-628X}]{Carl Boettiger}
\affil[1]{University of California, Berkeley, 130 Mulford Hall, Berkeley, CA 94720-3114 USA}

### 2020-09-15 rescience/article.Rmd
include intermediate tex add installation to Makefile

@@
   pdf_document:
+    keep_tex: true
     latex_engine: xelatex

### 2020-09-15 rescience/article.tex
include intermediate tex add installation to Makefile

--- 2020-02-18 rescience/manuscript.tex
@@
 
-In this analysis I seek to reproduce the numerical results of (Boettiger,
-Dushoff, and Weitz 2010), which focuses on the evolutionary trajectory
-of species trait under selection, as predicted by the so-called
-``Canonical Equation'' of adaptive dynamics (Dieckmann and Law 1996).
-Theoretical work I present in the paper predicts the emergence of a
-`flutation enhancement' regime far from an evolutionary stable point,
-and suggests that the evolution of traits which start in this distant
-region would deviate substantially from the expected evolutionary path
-predicted by the canonical equation. In particular, the distribution of
-such trajectories could be bimodal, making the ``canonical'' path far
-from the most likely path. The details of this distribution cannot be
-solved for analytically however, so in this paper I resorted to an
-replicate exact stochastic simulations of the evolutionary model using a
-Gillespie algorithm (Gillespie 1977).
+In this analysis I seek to reproduce the numerical results of
+(Boettiger, Dushoff, and Weitz 2010), which focuses on the evolutionary
+trajectory of species trait under selection, as predicted by the
+so-called ``Canonical Equation'' of adaptive dynamics (Dieckmann and Law
+1996). Theoretical work I present in the paper predicts the emergence of
+a `fluctuation enhancement' regime far from an evolutionary stable
+point, and suggests that the evolution of traits which start in this
+distant region would deviate substantially from the expected
+evolutionary path predicted by the canonical equation. In particular,
+the distribution of such trajectories could be bimodal, making the
+``canonical'' path far from the most likely path. The details of this
+distribution cannot be solved for analytically however, so in this paper
+I resorted to an replicate exact stochastic simulations of the
+evolutionary model using a Gillespie algorithm (Gillespie 1977).
 
@@
 original deposit (on the GeorgiaTech website and Dryad). The GitHub
-version also lacked a copy of the \texttt{inst/} subdirectory, which
+version also lacked a copy of the \texttt{inst/} sub-directory, which
 contained a copy of the manuscript \texttt{.tex} file, original
@@
 
-The same strategy worked on MacOSX (Catalina) with \texttt{gsl} installed
-via Homebrew. I was able to update the original autoconf script by
-recalling that it had been adapted from another package, the
+The same strategy worked on MacOSX (Catalina) with \texttt{gsl}
+installed via Homebrew. I was able to update the original autoconf
+script by recalling that it had been adapted from another package, the
 \texttt{gsl} R package
@@
 files \texttt{fig1.R} and \texttt{fig2.R} are were included in the same
-subdirectory as the \texttt{pdf} figures referenced by the \texttt{tex}
-version of the manuscript, but these files
-contained only the code required to actually generate the figures
-themselves once the result data had been pre-computed and saved as
-\texttt{.txt} files. The result data files had also not been archived
-separately. Fortunately, re-reading my own documentation, I was able to
-deduce that these text files were generated by running the function
-\texttt{logistic()} with the parameter settings given in the caption of
-Fig 2 in the manuscript.
+sub-directory as the \texttt{pdf} figures referenced by the \texttt{tex}
+version of the manuscript, but these files contained only the code
+required to actually generate the figures themselves once the result
+data had been pre-computed and saved as \texttt{.txt} files. The result
+data files had also not been archived separately. Fortunately,
+re-reading my own documentation, I was able to deduce that these text
+files were generated by running the function \texttt{logistic()} with
+the parameter settings given in the caption of Fig 2 in the manuscript.
 
@@
 \KeywordTok{landscape}\NormalTok{(logistic_curve, }\DecValTok{-3}\NormalTok{, }\DecValTok{3}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/fig1-1.pdf}
-\caption{The three panels of figure 1, showing examples of evolutionary
-landscapes and the corresponding fluctuation domains for three classic
-models (logistic, chemostat, branching model). This figure is largely
-theoretical, and so easily replicates Figure 1 of the original paper.
-The first panel showing the logistic model depicts the fluctuation
-regimes for the model parameters used in the numerical analysis.}
-\end{figure}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \KeywordTok{landscape}\NormalTok{(chemostat_curve, }\DecValTok{1}\NormalTok{, }\DecValTok{9}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/fig1-2.pdf}
-\caption{The three panels of figure 1, showing examples of evolutionary
-landscapes and the corresponding fluctuation domains for three classic
-models (logistic, chemostat, branching model). This figure is largely
-theoretical, and so easily replicates Figure 1 of the original paper.
-The first panel showing the logistic model depicts the fluctuation
-regimes for the model parameters used in the numerical analysis.}
-\end{figure}
-
-\begin{Shaded}
-\begin{Highlighting}[]
 \KeywordTok{landscape}\NormalTok{(branching_curve, }\FloatTok{-.8}\NormalTok{, }\FloatTok{.8}\NormalTok{)}
@@
 \begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/fig1-3.pdf}
-\caption{The three panels of figure 1, showing examples of evolutionary
-landscapes and the corresponding fluctuation domains for three classic
-models (logistic, chemostat, branching model). This figure is largely
-theoretical, and so easily replicates Figure 1 of the original paper.
-The first panel showing the logistic model depicts the fluctuation
-regimes for the model parameters used in the numerical analysis.}
+\includegraphics{article_files/figure-latex/fig1-1} \includegraphics{article_files/figure-latex/fig1-2} \includegraphics{article_files/figure-latex/fig1-3} \caption{The three panels of figure 1, showing examples of evolutionary landscapes and the corresponding fluctuation domains for three classic models (logistic, chemostat, branching model).
+This figure is largely theoretical, and so easily replicates Figure 1 of the original paper.
+The first panel showing the logistic model depicts the fluctuation regimes for the model parameters used in the numerical analysis.}\label{fig:fig1}
 \end{figure}
@@
 text. The C function does not expose a random seed, so re-running the
-analysis creates results which are not bitwise identical each time. Of
+analysis creates results which are not bit-wise identical each time. Of
 course the scientific results are expected to be independent of the seed
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
+\includegraphics{article_files/figure-latex/unnamed-chunk-2-1.pdf}
 \caption{A starting condition of Xo = 1, at the edge of the fluctuation
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{article_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{A starting condition of Xo = 2, matching the trajectories seen
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{article_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{Starting deep in the predicted fluctuation enhancement regime,
@@
   engines, and not use their own methods, which allows them to
-  coordinate with standard R methods for setting seed and so forth.\\
+  coordinate with standard R methods for setting seed and so forth.
 \item
   Data should be passed by reference back to R and not serialized to
-  disk (though this can introduce memory constraints).\\
+  disk (though this can introduce memory constraints).
 \item
   It is now also standard practice to register the C routines
-  explicitly.\\
+  explicitly.
 \item
@@
 
-Note that these tighter integrations would also prevent the C libraries
+Note that these tighter integration would also prevent the C libraries
 from running as purely stand-alone implementation. In any event, meeting
@@
 results. As the original results were not performed with a fixed random
-seed, replicated results are statistically comparable but not bitwise
+seed, replicated results are statistically comparable but not bit-wise
 identical. In a scientific sense this is perhaps more useful than
@@
 \leavevmode\hypertarget{ref-rmarkdown}{}%
-Xie, Yihui, J.J. Allaire, and Garrett Grolemund. 2018. \emph{R Markdown:
-The Definitive Guide}. Boca Raton, Florida: Chapman; Hall/CRC.
+Xie, Yihui, J. J. Allaire, and Garrett Grolemund. 2018. \emph{R
+Markdown: The Definitive Guide}. Boca Raton, Florida: Chapman; Hall/CRC.
 \url{https://bookdown.org/yihui/rmarkdown}.
